Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-15 Latex/journal_v1/V5/pr.tex
add code

Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 20 PRB

@@

  Minimum data rate for eMBB &  30 bits/sec/Hz \\ 

@@

In Fig. \ref{fig:1} the aggregated throughput is demonstrated versus different number of UEs in each service for these three methods. Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $35.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increase, but due to interference, it will decrease from 8 UEs to 10 UEs in each service.

@@

    \includegraphics[scale = 0.45]{rate_throuput.eps}

>>>>

Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 25 PRB

@@

  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 

@@

In Fig. \ref{fig:1} the aggregated throughput is demonstrated versus different number of UEs in each service for these three methods. Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increase, but due to the interference and the power constraint, it will saturated from 12 UEs in each service.

@@

    \includegraphics[scale = 0.45]{rate_ue1.eps}
